---
title: "00_preprocessing_auto"
author: "anjie"
date: "`r Sys.Date()`"
output: html_document
---


```{r}
library(tidyverse)
library(here)
library(jsonlite)

source(here("helper/combine_and_trim.R"))
source(here("helper/get_demog.R"))

```


# Merge & Trim 

DO NOT RUN (raw files do not live on github repo)

```{r eval=FALSE, include=FALSE}

cn_auto_d_row <- count_rows_for_files(here("data/00_raw_data/auto/data_M/"))
us_auto_d_row <- count_rows_for_files(here("data/00_raw_data/auto/data_E/"))
cn_auto_d <- trim_data(cn_auto_d_row, min_row = 15)
us_auto_d <- trim_data(us_auto_d_row, min_row = 15)

write_csv(cn_auto_d, here("data/00_raw_data/auto/raw_M.csv"))
write_csv(us_auto_d, here("data/00_raw_data/auto/raw_E.csv"))

```



# Get file created time 

```{r}
raw_files <- c(
  str_c(here("data/00_raw_data/auto/data_E/"), dir(here("data/00_raw_data/auto/data_E/"), "*.csv")),
  str_c(here("data/00_raw_data/auto/data_M/"), dir(here("data/00_raw_data/auto/data_M/"), "*.csv"))
  
)
  
auto_file_date_df <- tibble(
  raw_file_paths = raw_files
) %>% 
  rowwise() %>% 
  mutate(
    subject_id = gsub("-", "", gsub(".csv", "",regmatches(raw_file_paths, gregexpr("-([^.]+)\\.csv", raw_file_paths, perl=FALSE))[[1]])), 
    created_date = file.info(raw_file_paths)$mtime
  )


write_csv(auto_file_date_df, here("data/01_processed_data/auto_file_date.csv"))

```



# Get Clean Demog

```{r}
cn_auto_d <- read_csv(here("data/00_raw_data/auto/raw_M.csv"))
us_auto_d <- read_csv(here("data/00_raw_data/auto/raw_E.csv"))


cn_clean_demog <- lapply(na.omit(unique(cn_auto_d$subject)), function(x){
  print(x)
  get_tidy_demog(cn_auto_d %>% filter(subject == x))
}) %>% 
  bind_rows()


us_clean_demog <- lapply(na.omit(unique(us_auto_d$subject)), function(x){
  print(x)
  get_tidy_demog(us_auto_d %>% filter(subject == x))
}) %>% 
  bind_rows()

write_csv(cn_clean_demog, here("data/01_processed_data/auto/demog_M.csv"))
write_csv(us_clean_demog, here("data/01_processed_data/auto/demog_E.csv"))

```


# Get Exclusion 

```{r}
cn_auto_d <- read_csv(here("data/00_raw_data/auto/raw_M.csv"))
us_auto_d <- read_csv(here("data/00_raw_data/auto/raw_E.csv"))

cn_demog_d <-  read_csv(here("data/01_processed_data/auto/demog_M.csv"))
us_demog_d <-  read_csv(here("data/01_processed_data/auto/demog_E.csv"))

```
## RMTS side bias


```{r}
side_bias_df <- bind_rows(
  cn_auto_d %>% mutate(culture = "CN"), 
  us_auto_d %>% mutate(culture = "US")
) %>% 
  filter(trial_type == "rmts-test") %>% 
  group_by(subject, choice) %>% 
  count() %>% 
  filter(n == 4) %>%
  ungroup() %>% 
  select(subject) %>% 
  mutate(ex_reason = "side_bias")
 
```


## Regions lived more than 6 months at age 2 

 "<b>你曾在下列哪个（些）地区居住过两年及以上？请选择所有适用的选项。</b>"
 ["北美洲","南美洲", "欧洲", "非洲", "亚洲", "澳洲", "其它"]
 
 "<b>Which region(s) have you lived in for at least 2 years? Check all that apply.</b>"
 ["North America","South America", "Europe", "Africa", "Asia", "Australia", "Other"]

```{r}

live_abroad_df <- bind_rows(
  cn_demog_d %>% mutate(culture = "CN"), 
  us_demog_d %>% mutate(culture = "US")
) %>% 
  filter(demog_question == "which_regions") %>% 
  filter(demog_response %in% c("北美洲", "南美洲",  "欧洲", "澳洲", 
                                "Asia")) %>% 
  select(subject, id) %>% 
  mutate(ex_reason = "living_abroad")



```

## language speaking & understanding



```{r}

language_df <- bind_rows(
  cn_demog_d %>% mutate(culture = "CN"), 
  us_demog_d %>% mutate(culture = "US")
) %>% 
  filter(demog_question == "Q0" | demog_question == "Q1") %>% 
  filter(demog_response >= 3) %>%  
  select(subject, id) %>% 
  mutate(ex_reason = "language")
```

## from notes 

```{r}
extra_df <- tibble(
  ex_reason = c("ASD", "repeat_run", "missed_session","tech_error"), 
  subject = c(NA, NA, NA, NA),
  id = c("E111", "E98", "E23", "E88")
)
```



## put everything together 

```{r}
exclusion_table <- bind_rows(side_bias_df, live_abroad_df, language_df, extra_df)

write_csv(exclusion_table, here("data/01_processed_data/exclusion_table.csv"))
```


## link with the existing demog

```{r}

exclusion_table <- read_csv(here("data/01_processed_data/exclusion_table.csv"))

cn_hand_data <- read_csv(here("data/00_raw_data/hand_coded/cn_data.csv"))
us_hand_data <- read_csv(here("data/00_raw_data/hand_coded/us_data.csv"))
hand_demog <- read_csv(here("data/00_raw_data/hand_coded/demog_data.csv")) %>% 
  janitor::clean_names()


hand_data_with_age <- bind_rows(cn_hand_data %>% mutate(culture = "CN"), us_hand_data %>% mutate(culture = "US")) %>% 
  mutate(subject_id = str_replace_all(subject_id, c("_00"='', "_0"='', "E_"='E', "M_"='M'))) %>%
  left_join(hand_demog %>% rename(subject_id = subject_id_orig)) %>% 
  filter(years < 10)


exclusion_from_auto <- exclusion_table %>% 
  filter(!is.na(id)) %>% 
  filter(grepl("M", id) | grepl("E", id)) %>% 
  mutate(country = case_when(
    grepl("M", id) ~ "CN", 
    grepl("E", id) ~ "US"
  )) %>% 
  distinct( ex_reason, id, country)


exclusion_with_missing_file <- exclusion_table %>% 
  filter(is.na(id)) %>% 
  distinct(subject, ex_reason)

```

# check trigger condition 

```{r}

# calculate how many in each 


subject_n = hand_data_with_age %>% 
  distinct(subject_id, culture) %>% 
  group_by(culture) %>% 
  count() %>% 
  rename(total_n= n, country = culture)

# calculate how many excluded 

exclusion_from_auto %>% 
  group_by(country, ex_reason) %>% 
  count() %>% 
  left_join(subject_n, by = "country") %>% 
  mutate(percent = n / total_n)

exclusion_with_missing_file

```


