---
title: "kidculture analysis"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(readxl)
require(stringr)
require(ggpubr)
require(lme4)
require(tidyverse)
require(ggplot2)
require(here)
```

## Load data

```{r load-data, echo=F}
# view sheets
#readxl::excel_sheets("data/data_22Jan2023.xlsx") <-final data from last year
readxl::excel_sheets("data/data_18Jan2024.xlsx")

d_us <- read_xlsx("data/data_18Jan2024.xlsx", sheet="US")
d_cn <- read_xlsx("data/data_18Jan2024.xlsx", sheet="CN")
demog <- read_xlsx("data/data_18Jan2024.xlsx", sheet="demog") #just age in months, gender

fd_us <- read_xlsx("data/data_18Jan2024.xlsx", sheet="M&N FD generated CN")
fd_cn <- read_xlsx("data/data_18Jan2024.xlsx", sheet="M&N FD generated")
```


```{r, echo=FALSE}
#make main data, with everything but full FD coding (a la Masuda & Nisbett)
d <- d_us %>% dplyr::select(subject_id, task_type, trial_number, coder,
                     `responses (can also be NC, non-codeable)`) %>%
  mutate(country = "US") %>% 
  bind_rows(d_cn %>% dplyr::select(subject_id, task_type, trial_number, coder,
                     `responses (can also be NC, non-codeable)`) %>%
  mutate(country = "CN")) %>%
  rename(resp = `responses (can also be NC, non-codeable)`) %>%
  mutate(subject_id = str_replace_all(subject_id, c("_00"='', "_0"='', "E_"='E', "M_"='M'))) %>%
  left_join(demog) %>%
  mutate(months=replace_na(months,0)) %>%
  mutate(age = years * 12 + months) %>%
  #dplyr::select(-months) %>%
  filter(!is.na(subject_id))

#REMOVE REDUNDANT ENTRIES (when same kid coded more than once)
d$coder_index = NA #all coders set as NA, next we'll count them
for(s in unique(d$subject_id)) { #for each redundantly coded kid,
  sub_inds = which(d$subject_id==s) #get row nums for kid
  coders = unique(d[sub_inds,]$coder) #get coder names
  for(i in 1:length(coders)) {
    d[which(d$subject_id==s & d$coder==coders[i]),]$coder_index = (length(coders)+1)-i #number coders in reverse
  }
}

d <- d %>% filter(coder_index==1) #remove redundant entries (always retain the most recent coder)
# sort(table(d$subject_id)) #check if there are redundancies; length should be 14

#are any ppts are missing ages?
length(unique(d_us$subject_id)) # 122
length(unique(d_cn$subject_id)) # 101
#122+101 = 223 coded ppts
length(unique(d$subject_id)) # 220 after the joins, so 2 are missing from age list?

d_old <- subset(d, years>=10) # 57 kids from older group. who's missing? should be 38 US / 22 CN = 60

d <- d %>% filter(!is.na(age)) 
length(unique(d$subject_id)) # 220 (no age=na)

#make full FD tbl (a la Masuda & Nisbett)
fd <- fd_us %>% dplyr::select(subject_id, task_type, trial_number, response_type,
                     focal_count, objects_count, background_count, ambig_count, full_desc_coder) %>%
  mutate(country = "US") %>% 
  bind_rows(fd_cn %>% dplyr::select(subject_id, task_type, trial_number, response_type,
                     focal_count, objects_count, background_count, ambig_count, full_desc_coder) %>%
  mutate(country = "CN")) %>%
  mutate(subject_id = str_replace_all(subject_id, c("_00"='', "_0"='', "E_"='E', "M_"='M'))) %>%
  left_join(demog) %>%
  mutate(months=replace_na(months,0)) %>%
  mutate(age = years * 12 + months) %>%
  dplyr::select(-months) %>% #delete these columns
  filter(!is.na(subject_id)) %>%
  filter(task_type=="FD")


#REMOVE REDUNDANT ENTRIES (when same kid coded more than once)
fd$coder_index = NA #all coders set as NA, next we'll count them
for(s in unique(fd$subject_id)) { #for each redundantly coded kid,
  sub_inds = which(fd$subject_id==s) #get row nums for kid
  coders = unique(fd[sub_inds,]$full_desc_coder) #get coder names
  for(i in 1:length(coders)) {
    fd[which(fd$subject_id==s & fd$full_desc_coder==coders[i]),]$coder_index = (length(coders)+1)-i #number coders in reverse
  }
}

fd <- fd %>% filter(coder_index==1) #remove redundant entries (always retain the most recent coder)
# sort(table(fd$subject_id)) #check if there are redundancies; length should be 70

```

Loaded demographic data from `r length(unique(demog$subject_id))` participants.
Loaded coded data from `r length(unique(d$subject_id))` participants.

Age breakdown:

```{r}

#d %>% distinct(subject_id, country) %>% group_by(country) %>% count() %>% saveRDS(here("cached_data/demog_raw_country.Rds"))

d %>% group_by(subject_id, years, country) %>%
  summarise(n=n()) %>%
  group_by(years, country) %>%
  summarise(n=n())

#quick counts
youngUS <- d %>% filter(years<7,country=="US") %>% distinct(subject_id) # 39
midUS <- d %>% filter(years>=7 & years<10,country=="US") %>% distinct(subject_id) # 45 (was 43)
oldUS <- d %>% filter(years>=10,country=="US") %>% distinct(subject_id) # 37

youngCN <- d %>% filter(years<7,country=="CN") %>% distinct(subject_id) # 41 (was 42)
midCN <- d %>% filter(years>=7 & years<10,country=="CN") %>% distinct(subject_id) # 38
oldCN <- d %>% filter(years>=10,country=="CN") %>% distinct(subject_id) # 20

#US ppt lists
youngUS <- d %>% filter(years<7,country=="US")
youngUS = unique(youngUS$subject_id)

midUS <- d %>% filter(years>=7 & years<10,country=="US")
midUS = unique(midUS$subject_id)

oldUS <- d %>% filter(years>=10,country=="US")
oldUS = unique(oldUS$subject_id)

#CN ppt lists
youngCN <- d %>% filter(years<7,country=="CN")
youngCN = unique(youngCN$subject_id)

midCN <- d %>% filter(years>=7 & years<10,country=="CN")
midCN = unique(midCN$subject_id)

oldCN <- d %>% filter(years>=10,country=="CN")
oldCN = unique(oldCN$subject_id)

```
## exclusions

```{r}

subjectExcludes <- read_csv("data/01_processed_data/exclusion_table_linked.csv") %>%
  filter(!is.na(id))

#make sideBias list for RMTS exclusions
sideBias <- subjectExcludes %>% filter(ex_reason=="side_bias")

#how many language exclusions from CN sample?
langCN <- subjectExcludes %>% filter(ex_reason=="language" & startsWith(id, "M"))

#how many ppts in CN sample?
totalCN <- d %>% filter(country=="CN")
CNppts = unique(totalCN$subject_id)

#if more than 20% of total CN sample would be excluded for language, drop CN lang exclusions (otherwise retain)
if(nrow(langCN) / length(CNppts) > .2) {
  idx = with(subjectExcludes, which(ex_reason=="language" & startsWith(id, "M")))
  subjectExcludes = subjectExcludes[-idx,]
}

#remove the side bias exclusion rows so subjectExcludes contains only ppts who should be FULLY excluded for demog reasons
subjectExcludes <- subjectExcludes %>% filter(ex_reason!="side_bias")

length(unique(d$subject_id)) #221

d <- d %>% filter(!is.element(subject_id, subjectExcludes$id))

length(unique(d$subject_id)) #205

#make language category that distinguishes between CN ppts who are/are not bilingual in English
d <- d %>% mutate(language=ifelse(is.element(subject_id, langCN$id), "CN_ENG", country))


d %>% distinct(subject_id, age, country) %>% 
  filter(age <= 48) %>% 
  group_by(country) %>% 
  count() %>% saveRDS(here("cached_data/demog_youngkids.Rds"))

d %>% distinct(subject_id, gender, country) %>% 
  group_by(country, gender) %>% 
  count() %>% 
  saveRDS(here("cached_data/demog_gender.Rds"))

d %>% group_by(subject_id, language) %>%
  summarise(n=n()) %>%
  group_by(language) %>%
  summarise(n=n())
```

```{r}
d %>% filter(gender == "NA")
```


## RMTS

```{r}
#results summary: 
### all 4 trials: no effect of country, both near chance in youngest children, then move to ~75% performance between 60 and 100m, then track back to chance for the oldest kids, matching adult performance
### first trial: performance looks a little different by country, still no effect in main regression but fit is polynomial for US and not for CN. Eng bilinguals in CN are qualitatively very similar to US and unlike CN monolinguals

d_rmts <- d %>% filter(task_type=="RMTS") 

#clean up resp coding
d_rmts[which(d_rmts$resp=="relational"),]$resp = "relation"
d_rmts[which(d_rmts$resp=="obejct"),]$resp = "object"
d_rmts[which(d_rmts$resp=="n/a"),]$resp = NA
d_rmts[which(d_rmts$resp=="NA"),]$resp = NA

#check resp cleaning
unique(d_rmts$resp)

d_rmts <- d_rmts %>% 
  mutate(object_score = ifelse(resp=="object", 1, 
                             ifelse(resp=="relation", 0, NA)),
         across(c(subject_id, country), as.factor),
         trial_number = as.numeric(trial_number)) %>% 
    mutate(age_sc = scale(age))

#PREREG Ambiguous RMTS (logistic regression): choice ~ culture * age + (trial_num | subject). 
m_rmts <- glmer(object_score ~ country * age_sc + (trial_number | subject_id), 
                data = d_rmts,
                family = "binomial") #singular

m_rmts2 <- glmer(object_score ~ country * age_sc + (1 | subject_id), 
                data = d_rmts,
                family = "binomial") #only intercept
summary(m_rmts2)

#Because of concerns that children may (exploratorily) change their response strategy on later trials (2-4), we will also analyze first trial responding separately (logistic regression: choice ~ culture * age). If this first trials analysis produces results that differ significantly from our regression with all trials, we will rely on the first trial results for interpretation.
m_rmts_first <- glm(object_score ~ country * age_sc,
                      data = d_rmts %>% filter(trial_number == 1),
                      family = "binomial") #only intercept

summary(m_rmts_first)

#post hoc exploratory, theoretically motivated
#is there a curvilinear relationship bw age and performance?
m_rmts_first_curve <- glm(object_score ~ country * poly(age_sc, 2),
                      data = d_rmts %>% filter(trial_number == 1),
                      family = "binomial") #polynomial trending
summary(m_rmts_first_curve)

#is there a curvilinear relationship bw age and performance in US? YES
m_rmts_first_curve <- glm(object_score ~ poly(age_sc, 2),
                      data = d_rmts %>% filter(trial_number == 1) %>% filter(country == "US"),
                      family = "binomial") #poly(age_sc, 2)2
summary(m_rmts_first_curve)

#is there a curvilinear relationship bw age and performance in CN? NO
m_rmts_first_curve <- glm(object_score ~ poly(age_sc, 2),
                      data = d_rmts %>% filter(trial_number == 1) %>% filter(country == "CN"),
                      family = "binomial") #polynomial trending
summary(m_rmts_first_curve)

# main plot megaplot
d_rmts %>% filter(!is.na(object_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean = mean(object_score)) %>%
  mutate(Country = country,
         prop_relation = 1-mean) %>% #flips y axis
  ggplot(aes(x=jitter(age,.1), y=prop_relation, group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion choosing relational match") 
ggsave("RMTS_all_trials.pdf", width=6, height=3)


# main plot, CN bilinguals split out 
d_rmts %>% filter(!is.na(object_score)) %>%
  group_by(subject_id, language, age) %>%
  summarise(mean = mean(object_score)) %>% 
  mutate(prop_relation = 1-mean) %>% #flips y axis
  ggplot(aes(x=jitter(age,.1), y=prop_relation, group=language, color=language)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion choosing relational match") 

#first trial
d_rmts1 <- d_rmts %>% filter(trial_number==1) 
d_rmts1 %>% filter(!is.na(object_score)) %>%
  group_by(subject_id, country, age) %>%
  ggplot(aes(x=age, y=jitter((1-object_score),.1), group=country, color=country)) + #flips y axis
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Relational matching on first trial") 

#first trial, CN bilinguals split out 
d_rmts1 %>% filter(!is.na(object_score)) %>%
  group_by(subject_id, language, age) %>%
  ggplot(aes(x=age, y=jitter((1-object_score),.1), group=language, color=language)) + #flips y axis
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Relational matching on first trial") 

#mean perf looks similar across countries, but first response seems to show an object bias in the youngest US ppts

```

### Writing cache 

```{r}
library(here)
d_rmts %>% group_by(country) %>% summarise(mean_object_score = mean(object_score, na.rm = TRUE)) %>% mutate_if(is.numeric, round, 2) %>% saveRDS(here("cached_data/rmts_mean_all.Rds")) 

d_rmts %>% group_by(country) %>% filter(trial_number == 1) %>% summarise(mean_object_score = mean(object_score, na.rm = TRUE)) %>% mutate_if(is.numeric, round, 2) %>% saveRDS(here("cached_data/rmts_mean_first_trial.Rds")) 


broom.mixed::tidy(m_rmts_first_curve) %>% mutate_if(is.numeric, round, 2) %>%  saveRDS(here("cached_data/rmts_explore_model.Rds")) 
```



## Free Description, first mention

```{r}
#results summary: effect of country, US more focal, but both groups are quite biased toward focal. In language split plot, mono CN participants start veering toward the adult pattern at about 120 months

#clean up main FD data
d_fd <- d %>% filter(task_type=="FD")
d_fd[which(d_fd$resp=="NA"),]$resp = NA
d_fd[which(d_fd$resp=="N/A"),]$resp = NA
d_fd[which(d_fd$resp=="n/a"),]$resp = NA
d_fd[which(d_fd$resp=="Focal"),]$resp = "focal"

#check resp cleaning
unique(d_fd$resp)

d_fd <- d_fd %>% 
  mutate(focal_score = ifelse(resp=="focal", 1, 
                             ifelse(resp=="background", 0, NA))) %>% 
  mutate(age_sc = scale(age))

#PREREG: (a, logistic regression) first_mention ~ culture * age + (1 | subject) + (culture | scene)
#(b, Poisson regression) description_num ~ description_type * culture * age + (description_type | subject) + (culture | scene)
m_fd1 <- glmer(focal_score ~ country * age_sc + (1 | subject_id) + (country | trial_number),
              data = d_fd,
              family = "binomial") #singular
m_fd2 <- glmer(focal_score ~ country * age_sc + (1 | subject_id) + (1 | trial_number),
              data = d_fd,
              family = "binomial") #effect of country, US more focal mentions
summary(m_fd2)


# main plot megaplot
d_fd %>% filter(!is.na(focal_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean_focal = mean(focal_score)) %>%
  mutate(Country = country) %>%
  ggplot(aes(x=age, y=mean_focal, group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  ylim(0,1) + xlab("Age in months") + ylab("Proportion first mention focal")
ggsave("FD_firstMention.pdf", width=6, height=3)

# split out Eng bilinguals from CN
d_fd %>% filter(!is.na(focal_score)) %>%
  group_by(subject_id, language, age) %>%
  summarise(mean_focal = mean(focal_score)) %>%
  ggplot(aes(x=age, y=mean_focal, group=language, color=language)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  ylim(0,1) + xlab("Age in months") + ylab("Proportion first mention focal")

```

```{r}
# finding the effect size

m_fd2 <- glmer(focal_score ~ country * age_sc + (1 | subject_id) + (1 | trial_number),
              data = d_fd,
              family = "binomial") #

varcor_df <- summary(m_fd2)$varcor %>% 
  as.data.frame() %>% 
  filter(is.na(var2))

pooled_var <- sqrt(sum(varcor_df$vcov)) 
fixed_effect_df <- summary(m_fd2)$coefficients %>% 
    as.data.frame() %>% rownames_to_column("term_name") 

estimate <- fixed_effect_df %>% 
      filter(term_name == "countryUS") %>% 
      pull(Estimate)

smd <- estimate / pooled_var


```



#### writing cache 

```{r}
d_fd %>% group_by(country) %>% summarise(mean_score = mean(focal_score, na.rm = TRUE)) %>% mutate_if(is.numeric, round, 2) %>% write_rds(here("cached_data/fd_first_mention_mean.Rds"))

m_fd2 %>% broom.mixed::tidy() %>% mutate_if(is.numeric, round, 2) %>% write_rds(here("cached_data/fd_first_mention_model.Rds"))

smd %>% write_rds(here("cached_data/fd_smd.Rds"))
```


## Free Description, full description

```{r}
#results summary: 

#clean up M&N FD data
fd[which(is.element(fd$focal_count, c("NA","na","n/a"))),] = NA
fd[which(is.element(fd$objects_count, c("NA","na","n/a"))),] = NA
fd[which(is.element(fd$background_count, c("NA","na","n/a"))),] = NA

#check resp cleaning
unique(fd$focal_count)
unique(fd$objects_count)
unique(fd$background_count)


fd_full <- fd %>% 
  mutate(focal_count = as.numeric(focal_count),
         objects_count = as.numeric(objects_count),
         background_count = as.numeric(background_count),
         non_focal = objects_count + background_count,
         age_sc = scale(age)) %>% 
  filter(response_type!="first_mention") #remove first mention coding since we looked at that above


#PREREG: (b, Poisson regression) description_num ~ description_type * culture * age + (description_type | subject) + (culture | scene)
#description_num = per-trial count of descriptions referring to the focal object vs. anything else

fd_sum <- fd_full %>%
  filter(!is.element(response_type,c("location", "relation_to_moveable", "relation_to_inert", "time"))) %>%
  group_by(subject_id, trial_number, country, age_sc, age) %>%
  summarise(focal = sum(focal_count),
            non_focal = sum(non_focal)) %>%
  pivot_longer(cols = c("focal","non_focal"), names_to = "desc_type", values_to = "desc_num")


# m_fdb <- glmer(desc_num ~ desc_type * country * age_sc + (desc_type | subject_id) + (country | trial_number),
#               data = fd_sum,
#               family = "poisson") ##isSingular

# m_fdb <- glmer(desc_num ~ desc_type * country * age_sc + (1 | subject_id) + (country | trial_number),
#               data = fd_sum,
#               family = "poisson") ##isSingular

m_fdb <- glmer(desc_num ~ desc_type * country * age_sc + (desc_type | subject_id) + (1 | trial_number),
              data = fd_sum,
              family = "poisson")

summary(m_fdb)

# full data plot:
fd_sum %>% filter(!is.na(desc_num)) %>%
  group_by(subject_id, country, age_sc, age, desc_type) %>%
  summarise(mean_desc_num = mean(desc_num)) %>%
  mutate(Country = country) %>% 
  ggplot(aes(x=age, y=mean_desc_num, group=desc_type, color=desc_type)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  facet_wrap(. ~ Country) +
  xlab("Age in months") + ylab("Number of descriptions")

# proportion plot (easier to interpret):
fd_full %>% #filter(!is.na(focal_prop)) %>%
  group_by(subject_id, country, age_sc, age) %>%
  summarise(focal = sum(focal_count),
            non_focal = sum(non_focal),
            focal_prop = focal/(focal+non_focal)) %>%
  mutate(Country = country) %>% 
  ggplot(aes(x=age, y=focal_prop, group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion focal descriptions")

# split out Eng bilinguals from CN?

```

```{r}
m_fdb  %>% broom.mixed::tidy() %>% mutate_if(is.numeric, round, 2)
```


## Causal Attribution

```{r, causal-attribution}
d_ca <- d %>% filter(task_type=="CA")

d_ca[which(d_ca$resp=="0"),]$resp = "scared"
d_ca[which(d_ca$resp=="personal"),]$resp = "person"
d_ca[which(d_ca$resp=="NA"),]$resp = NA
d_ca[which(d_ca$resp=="n/a"),]$resp = NA

#check resp cleaning 
unique(d_ca$resp) #22jan24 cleaning needed

d_ca <- d_ca %>% # filter(!is.na(resp)) %>%
  mutate(n_person = str_count(d_ca$resp, "person"),
         n_situation = str_count(d_ca$resp, "situation"),
         n_scared = str_count(d_ca$resp, "scared")) %>%
  mutate(person_focus = n_person - n_situation,
         person_scared = n_person + n_scared - n_situation,
         person_prop = n_person/(n_person+n_situation),
         situation_prop = n_situation/(n_person+n_situation)) %>%
  mutate(age_sc = scale(age))

d_ca$trial_number = as.numeric(d_ca$trial_number)

#PREREG (Poisson regression): situation_attrib_num ~ culture * age + (1 | subject) + (culture | trial)
m_ca <- glmer(n_situation ~ country * age_sc + (1 | subject_id) + (country | trial_number),
              data = d_ca,
              family = "poisson") #singular fit
m_ca2 <- glmer(n_situation ~ country * age_sc + (1 | subject_id) + (1 | trial_number),
              data = d_ca,
              family = "poisson") #singular fit
m_ca3 <- glmer(n_situation ~ country * age_sc + (1 | subject_id),
              data = d_ca,
              family = "poisson") #effect of country and age
summary(m_ca3)

#not in the prereg but seems like a useful complement (adult literature suggests similar person bias in US/CN but worth checking anyway)
m_ca_person <- glmer(n_person ~ country * age_sc + (1 | subject_id) + (country | trial_number),
              data = d_ca,
              family = "poisson") #singular fit
m_ca_person2 <- glmer(n_person ~ country * age_sc + (1 | subject_id) + (1 | trial_number),
              data = d_ca,
              family = "poisson") #singular fit
m_ca_person3 <- glmer(n_person ~ country * age_sc + (1 | subject_id),
              data = d_ca,
              family = "poisson") 
summary(m_ca_person3) #age (more person atts with age)

#main plot, megaplot
p1 <- d_ca %>% mutate(Country = country) %>%
  ggplot(aes(x = age, y = jitter(person_prop), group = Country, color = Country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion person attributions") + 
  theme(legend.position = "right")
  #theme(legend.position = c(0.8, 0.2)) # more control (x,y = [0,1])
ggsave("PersonAtt.pdf", width=6, height=3)

p2 <- d_ca %>% mutate(Country = country) %>%
  ggplot(aes(x = age, y = jitter(situation_prop), group = Country, color = Country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion situation attributions") + 
  theme(legend.position = "right")
  #theme(legend.position = c(0.8, 0.2)) # more control (x,y = [0,1])
ggsave("SituationAtt.pdf", width=6, height=3)

p1
ggarrange(p1, p2, common.legend = T)

#check how scared coding is working (person_scared = n_person + n_scared - n_situation)
p3 <- d_ca %>% mutate(Country = country) %>%
  ggplot(aes(x = age, y = jitter(person_scared), group = Country, color = Country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age (months)") + ylab("Person scared")
p3

#person focus (person_focus = n_person - n_situation)
p4 <- d_ca %>% mutate(Country = country) %>%
  ggplot(aes(x = age, y = jitter(person_focus), group = Country, color = Country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age (months)") + ylab("Person focus")

p4 #doesn't really help with verbose kids
```




```{r, causal-attribution-2}
#plot 2: instead plot n_person and n_situation
p1 <- d_ca %>% ggplot(aes(x = age, y = jitter(n_person), group = country, color = country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age (months)") + ylab("N Person")

p2 <- d_ca %>% ggplot(aes(x = age, y = jitter(n_situation), group = country, color = country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() + 
  xlab("Age (months)") + ylab("N situation")

ggarrange(p1, p2, common.legend = T)
```


```{r, causal-attribution-3, eval=FALSE}
pl1 <- d_ca %>% ggplot(aes(x = age, y = jitter(person_focus), group = language, color = language)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic()

pl2 <- d_ca %>% ggplot(aes(x = age, y = jitter(person_scared), group = language, color = language)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic()

ggarrange(pl1, pl2, common.legend = T)
```

### writing cache 

```{r}
d_ca %>% group_by(country) %>% summarise(mean = mean(n_situation, na.rm = TRUE)) %>% mutate_if(is.numeric, round, 2) %>% saveRDS(here("cached_data/ca_situational_mean.Rds"))

m_ca3 %>% broom.mixed::tidy() %>% mutate_if(is.numeric, round, 2) %>% saveRDS(here("cached_data/ca_model.Rds"))
```


## Uniqueness Preference

```{r}
d_up <- d %>% filter(task_type=="UP") 

d_up[which(d_up$resp=="non_unique"),]$resp = "non-unique"
d_up[which(d_up$resp=="n/a"),]$resp = NA
d_up[which(d_up$resp=="NA"),]$resp = NA

#check resp cleaning
unique(d_up$resp)

d_up <- d_up %>% 
  mutate(unique = ifelse(resp=="unique", 1, 
                             ifelse(resp=="non-unique", 0, NA))) %>% 
  mutate(age_sc = scale(age))

#PREREG (logistic regression): choice ~ culture * age
m_up <- glm(unique ~ country * age_sc,
            data = d_up,
            family = "binomial") #sig effects of country (but in opposite direction, seems likely to be pragmatic helpfulness on the part of CN ppts--interesting result, but not the task we'd intended to run!)
summary(m_up)

#main plot megaplot
d_up %>% filter(!is.na(unique)) %>%
  mutate(Country = country) %>%
  group_by(subject_id, country, age) %>%
  ggplot(aes(x=age, y=jitter(unique,.2), group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  ylim(0,1) + xlab("Age in months") + ylab("Preference for unique option") +
  scale_y_continuous(limits = c(0,1.2), breaks= seq(0,1.2,.25))
ggsave("Uniqueness.pdf", width=6, height=3)

d_up %>% filter(!is.na(unique)) %>%
  group_by(subject_id, language, age) %>%
  ggplot(aes(x=age, y=jitter(unique,.2), group=language, color=language)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic()
```

### writing cache

```{r}
d_up %>% group_by(country) %>% summarise(mean = mean(unique, na.rm = TRUE)) %>% mutate_if(is.numeric, round, 2) %>% saveRDS(here("cached_data/up_mean.Rds"))

m_up %>% broom.mixed::tidy() %>% mutate_if(is.numeric, round, 2) %>% saveRDS(here("cached_data/up_model.Rds"))
```





## Relationships between tasks
From PREREG:
2. How do cross-cultural differences relate across these tasks? In particular, do the social tasks (2-3) pattern together, showing more similar responses within than across domains?
3. More specifically, do cross-cultural differences in visual attention (1) or reasoning about social relations (2-3) correlate with or mediate [country/age effect on] performance in relational reasoning (4)?

```{r}
#TLDR: nothing
#merge cleaned datasets back together
d_all <- d_up %>% select(subject_id, country, age_sc, age, years, unique) %>%
  left_join(d_rmts %>% arrange(subject_id, trial_number) %>%
              group_by(subject_id) %>% 
              summarise(object_score = mean(object_score))) %>% # object_score1 = slice_head(object_score, n=1), 
  left_join(d_fd %>% group_by(subject_id) %>% 
              summarise(focal_score = mean(focal_score))) %>% 
  left_join(d_ca %>% group_by(subject_id) %>% 
              summarise(person_prop = mean(person_prop))) %>%
  left_join(d_rmts %>% filter(trial_number==1) %>% 
              rename(object_first = object_score) %>% select(subject_id, object_first))


#do social tasks (UP & CA) pattern together? nah
cor.test(d_all$unique, d_all$person_prop, na.rm=T) #no correlation

social <- lm(person_prop ~ country * age_sc * unique,
            data = d_all)
summary(social) #country effect only; no effect of UP in predicting CA

social2 <- glm(unique ~ country * age_sc * person_prop,
            data = d_all,
            family = "binomial")
summary(social2) #trending interactions: country*person_prop(CA), age*person_prop(CA)

d_all %>% ggplot(aes(x=age, y=person_prop, group=as.factor(country), color=as.factor(country))) + 
  facet_wrap(. ~ unique) +
  geom_point() #nothing clear

# how does RR relate to other tasks? not

#corrs
cor.test(d_all$object_score, d_all$unique, na.rm=T) #no correlation
cor.test(d_all$object_score, d_all$person_prop, na.rm=T) #no correlation
cor.test(d_all$object_score, d_all$focal_score, na.rm=T) #trending correlation

RR_pens <- lm(object_score ~ country * age_sc * unique, 
            data = d_all)
summary(RR_pens) #trending 3-way countryUS:age_sc:unique

RR_attrib <- lm(object_score ~ country * age_sc * person_prop, 
            data = d_all)
summary(RR_attrib) #intercept only

RR_fish <- lm(object_score ~ country * age_sc * focal_score, 
            data = d_all)
summary(RR_fish) #nada

#pens plot
d_all %>% ggplot(aes(x=age, y=object_score, group=as.factor(country), color=as.factor(country))) + 
  facet_wrap(. ~ unique) +
  geom_point() #nothing clear

#mediation: no country/age effects on RMTS, so no relationship to be mediated

```



# Make mega plot 

```{r}
#prop_relation
plot_rmds_d <- d_rmts %>% filter(!is.na(object_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean = mean(object_score)) %>%
  mutate(Country = country,
         prop_relation = 1-mean) %>% 
  rename(response = prop_relation) %>% 
  mutate(task = "RMTS")

#mean_focal
plot_fd_d <- d_fd %>% filter(!is.na(focal_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean_focal = mean(focal_score)) %>%
  mutate(Country = country) %>% 
  rename(response = mean_focal) %>% 
  mutate(task = "Free Description")

#unique
plot_up_d <- d_up %>% filter(!is.na(unique)) %>%
  mutate(Country = country) %>%
  group_by(subject_id, country, age) %>% 
  rename(response = unique) %>% 
  mutate(trial_number = as.character(trial_number)) %>% 
  mutate(task = "Uniqueness Preference")

#person_prop
plot_ca_d <-  d_ca %>% mutate(Country = country) %>% 
  rename(response = person_prop) %>% 
  mutate(trial_number = as.character(trial_number)) %>% 
  mutate(task = "Causal Attribution")





# Make Mega Plot
bind_rows(plot_rmds_d, plot_fd_d, plot_up_d, plot_ca_d) %>% 
  mutate(task = factor(task, levels = c("RMTS", "Free Description", "Uniqueness Preference", "Causal Attribution"))) %>% 
  ggplot(aes(x=jitter(age,.1), y=response, group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  scale_color_manual(values = c("red", "blue")) + 
  facet_wrap(~task, scales = "free") + 
  xlab("Age in months") + 
  ylab("Proportion target response") + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "top")

  





  #flips y axisggplot(aes(x=jitter(age,.1), y=prop_relation, group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion choosing relational match") 

plot_fd_d <- d_fd %>% filter(!is.na(focal_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean_focal = mean(focal_score)) %>%
  mutate(Country = country) + 
   xlab("Age in months")



%>%
  ggplot(aes(x=age, y=mean_focal, group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  ylim(0,1) + xlab("Age in months") + ylab("Proportion first mention focal")

d_up %>% filter(!is.na(unique)) %>%
  mutate(Country = country) %>%
  group_by(subject_id, country, age) %>%
  ggplot(aes(x=age, y=jitter(unique,.2), group=Country, color=Country)) + 
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  ylim(0,1) + xlab("Age in months") + ylab("Preference for unique option") +
  scale_y_continuous(limits = c(0,1.2), breaks= seq(0,1.2,.25))

 d_ca %>% mutate(Country = country) %>%
  ggplot(aes(x = age, y = jitter(person_prop), group = Country, color = Country)) +
  geom_point(alpha=.5) + geom_smooth() + theme_classic() +
  xlab("Age in months") + ylab("Proportion person attributions") + 
  theme(legend.position = "right")
  #theme(legend.position = c(0.8, 0.2)) # more control (x,y = [0,1])

```

```{r}


plot_rmds_d <- d_rmts %>% filter(!is.na(object_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean = mean(object_score)) %>%
  mutate(Country = country,
         prop_relation = 1-mean) %>% 
  rename(response = prop_relation) %>% 
  mutate(task = "RMTS")

#mean_focal
plot_fd_d <- d_fd %>% filter(!is.na(focal_score)) %>%
  group_by(subject_id, country, age) %>%
  summarise(mean_focal = mean(focal_score)) %>%
  mutate(Country = country) %>% 
  rename(response = mean_focal) %>% 
  mutate(task = "Free Description")

#unique
plot_up_d <- d_up %>% filter(!is.na(unique)) %>%
  mutate(Country = country) %>%
  group_by(subject_id, country, age) %>% 
  rename(response = unique) %>% 
  mutate(trial_number = as.character(trial_number)) %>% 
  mutate(task = "Uniqueness Preference")

#person_prop
plot_ca_d <-  d_ca %>% mutate(Country = country) %>% 
  rename(response = person_prop) %>% 
  mutate(trial_number = as.character(trial_number)) %>% 
  mutate(task = "Causal Attribution")


plot_d <- bind_rows(plot_rmds_d, plot_fd_d, 
                    plot_up_d, plot_ca_d)

saveRDS(plot_d, here("cached_data/plot_d.Rds"))



loess_span = 1




plot_rmts <- plot_d %>% 
  filter(task == "RMTS") %>% 
  ggplot(aes(x=jitter(age,.1), y=response, group=Country, color=Country)) + 
  geom_point(alpha=.5) + 
  geom_smooth(method = "loess", span = loess_span) + 
  theme_classic() +
  scale_color_manual(values = c("red", "blue")) + 
  #theme(legend.position = "none") +
  coord_cartesian(ylim = c(0, 1))+
  #xlab("Age in months") + 
  xlab("") +
  ylab("Proportion choosing relational match") + 
  labs(title = "RMTS") + 
theme(plot.title = element_text(hjust = 0.5, size = 9), 
      axis.title=element_text(size=8))


plot_fd <- plot_d %>% 
  filter(task == "Free Description") %>% 
  ggplot(aes(x=jitter(age,.1), y=response, group=Country, color=Country)) + 
  geom_point(alpha=.5) + 
  geom_smooth(method = "loess", span = loess_span) + 
  theme_classic() +
  scale_color_manual(values = c("red", "blue")) +
  coord_cartesian(ylim = c(0, 1))+
  #theme(legend.position = "none", 
  #      axis.title=element_text(size=8)) +
  #xlab("Age in months") +
  xlab("") +
  ylab("Proportion first mention focal") + 
  labs(title = "Free Description") + 
theme(plot.title = element_text(hjust = 0.5, size = 9), 
      axis.title=element_text(size=8))

plot_up <- plot_d %>% 
  filter(task == "Uniqueness Preference")  %>% 
  ggplot(aes(x=jitter(age,.1), y=response, group=Country, color=Country)) + 
  geom_point(alpha=.5) +  theme_classic() +
  geom_smooth(method = "loess", span = loess_span) + 
  scale_color_manual(values = c("red", "blue")) + 
  coord_cartesian(ylim = c(0, 1))+
 #theme(legend.position = "none", 
#        axis.title=element_text(size=8)) +
  #xlab("Age in months") + 
  xlab("") +
  ylab("Preference for unique option") +
   labs(title = "Uniqueness Preference") + 
 theme(plot.title = element_text(hjust = 0.5, size = 9), 
       axis.title=element_text(size=8))

plot_ca <- plot_d %>% 
  filter(task == "Causal Attribution")  %>% 
  ggplot(aes(x = age, y = jitter(response), group = Country, color = Country)) +
  geom_point(alpha=.5) + theme_classic() +
  geom_smooth(method = "loess", span = loess_span) + 
  scale_color_manual(values = c("red", "blue")) + 
  coord_cartesian(ylim = c(0, 1))+
  #theme(legend.position = "none", 
  #      axis.title=element_text(size=8)) +
 #xlab("Age in months") + 
  xlab("") +
  ylab("Proportion person attributions") + 
    labs(title = "Causal Attribution") + 
  theme(plot.title = element_text(hjust = 0.5, size = 9), 
        axis.title=element_text(size=8))


library(patchwork)

(plot_rmts + plot_fd) / (plot_ca + plot_up) + plot_layout(guides = 'collect') & theme(legend.position = "bottom") 
```


